\textbf{DiracDec C++/Coq Implementation\cite{ExampleCitation}}

### 2024-12-03 main.tex
updated ADJ rules

\begin{ruletable}{Rules for linear algebra addition. }
    %
    R-ADDID
    & $+(X) \ \reduce\ X$ \\
    & \textcolor{gray}{Reduce the term if the AC symbol $+$ only has one argument.} \\
    %
    R-ADD0
    & $a_1 + \cdots + X + \cdots + X + \cdots + a_n \ \reduce\ a_1 + \cdots + a_n + \cdots + (1+1).X$ \\
    & \textcolor{gray}{\makecell[l]{This rule matches the first $X$ in the list satisfying the pattern. \\ The result $(1+1).X$ will be placed at the end of the list.}} \\
    %
    R-ADD1
    & $a_1 + \cdots + X + \cdots + a.X + \cdots + a_n \ \reduce\ a_1 + \cdots + a_n + (1+a).X$ \\
    & \textcolor{gray}{Similar to (R-ADD0).} \\
    %
    R-ADD2
    & $a_1 + \cdots + a.X + \cdots + X + \cdots + a_n \ \reduce\ a_1 + \cdots + a_n + (a+1).X$ \\
    & \textcolor{gray}{Similar to (R-ADD0).} \\
    %
    R-ADD3
    & $a_1 + \cdots + a.X + \cdots + b.X + \cdots + a_n \ \reduce\ a_1 + \cdots + a_n + (a+b).X$ \\
    & \textcolor{gray}{Similar to (R-ADD0).} \\
    %
    R-ADDK0
    & $K_1 + \cdots + \ZEROK(\sigma) + \cdots + K_n\ \reduce K_1 + \cdots + K_n$ \\
    & \textcolor{gray}{Similar to (R-ADDS0).} \\
    %
    R-ADDB0
    & $B_1 + \cdots + \ZEROB(\sigma) + \cdots + B_n \ \reduce\ B_1 + \cdots + B_n$ \\
    & \textcolor{gray}{Similar to (R-ADDS0).} \\
    %
    R-ADDO0
    & $O_1 + \cdots + \ZEROO(\sigma, \tau) + \cdots + O_n \ \reduce\ O_1 + \cdots + O_n$ 
    \\
    & \textcolor{gray}{Similar to (R-ADDS0).} \\
\end{ruletable}

\begin{ruletable}{Rules for adjoint.}
    %
    R-ADJ0
    & $ (X^\dagger)^\dagger \ \reduce\ X $ \\
    %
    R-ADJ1
    & $ (a.X)^\dagger \ \reduce\ (a^*).(X^\dagger) $ \\
    %
    R-ADJ2
    & $ (X_1 + \cdots + X_n)^\dagger \ \reduce\ X_1^\dagger + \cdots + X_n^\dagger $ \\
    %
    R-ADJK0
    & $ \ZEROB(\sigma)^\dagger \ \reduce\ \ZEROK(\sigma) $ \\
    %
    R-ADJK1
    & $ \bra{t}^\dagger \ \reduce\ \ket{t} $ \\
    %
    R-ADJK2
    & $ (B \cdot O)^\dagger\ \reduce\ O^\dagger \cdot B^\dagger $ \\
    %
    R-ADJK3
    & $ (B_1 \otimes B_2)^\dagger \ \reduce\ B_1^\dagger \otimes B_2^\dagger $ \\
    %
    R-ADJB0
    & $ \ZEROK(\sigma)^\dagger \ \reduce\ \ZEROB(\sigma) $ \\
    %
    R-ADJB1
    & $ \ket{t}^\dagger \ \reduce\ \bra{t} $ \\
    %
    R-ADJB2
    & $ (O \cdot K)^\dagger\ \reduce\ K^\dagger \cdot O^\dagger $ \\
    %
    R-ADJB3
    & $ (K_1 \otimes K_2)^\dagger \ \reduce\ K_1^\dagger \otimes K_2^\dagger $ \\
    %
    R-ADJO0
    & $ \ZEROO(\sigma, \tau)^\dagger \ \reduce\ \ZEROO(\tau, \sigma) $ \\
    %
    R-ADJO1
    & $ \ONEO(\sigma)^\dagger \ \reduce\ \ONEO(\sigma)$ \\
    %
    R-ADJO2
    & $ (K \cdot B)^\dagger \ \reduce\ B^\dagger \cdot K^\dagger$ \\
    %
    R-ADJO3
    & $ (O_1 \cdot O_2)^\dagger \ \reduce\ O_2^\dagger \cdot O_1^\dagger $ \\
    %
    R-ADJO4
    & $ (O_1 \otimes O_2)^\dagger \ \reduce\ O_1^\dagger \otimes O_2^\dagger $ 
\end{ruletable}

>>>>

\begin{ruletable}{Rules for linear algebra addition. }
    %
    R-ADDID
    & $+(X) \ \reduce\ X$ \\
    & \textcolor{gray}{Reduce the term if the AC symbol $+$ only has one argument.} \\
    %
    R-ADD0
    & $Y_1 + \cdots + X + \cdots + X + \cdots + Y_n \ \reduce\ Y_1 + \cdots + Y_n + \cdots + (1+1).X$ \\
    & \textcolor{gray}{\makecell[l]{This rule matches the first $X$ in the list satisfying the pattern. \\ The result $(1+1).X$ will be placed at the end of the list.}} \\
    %
    R-ADD1
    & $Y_1 + \cdots + X + \cdots + a.X + \cdots + Y_n \ \reduce\ Y_1 + \cdots + Y_n + (1+a).X$ \\
    & \textcolor{gray}{Similar to (R-ADD0).} \\
    %
    R-ADD2
    & $Y_1 + \cdots + a.X + \cdots + X + \cdots + Y_n \ \reduce\ Y_1 + \cdots + Y_n + (a+1).X$ \\
    & \textcolor{gray}{Similar to (R-ADD0).} \\
    %
    R-ADD3
    & $Y_1 + \cdots + a.X + \cdots + b.X + \cdots + Y_n \ \reduce\ Y_1 + \cdots + Y_n + (a+b).X$ \\
    & \textcolor{gray}{Similar to (R-ADD0).} \\
    %
    R-ADDK0
    & $K_1 + \cdots + \ZEROK(\sigma) + \cdots + K_n\ \reduce K_1 + \cdots + K_n$ \\
    & \textcolor{gray}{Similar to (R-ADDS0).} \\
    %
    R-ADDB0
    & $B_1 + \cdots + \ZEROB(\sigma) + \cdots + B_n \ \reduce\ B_1 + \cdots + B_n$ \\
    & \textcolor{gray}{Similar to (R-ADDS0).} \\
    %
    R-ADDO0
    & $O_1 + \cdots + \ZEROO(\sigma, \tau) + \cdots + O_n \ \reduce\ O_1 + \cdots + O_n$ 
    \\
    & \textcolor{gray}{Similar to (R-ADDS0).} \\
\end{ruletable}

\begin{ruletable}{Rules for adjoint.}
    %
    R-ADJ0
    & $ (X^\dagger)^\dagger \ \reduce\ X $ \\
    %
    R-ADJ1
    & $ (a.X)^\dagger \ \reduce\ (a^*).(X^\dagger) $ \\
    %
    R-ADJ2
    & $ (X_1 + \cdots + X_n)^\dagger \ \reduce\ X_1^\dagger + \cdots + X_n^\dagger $ \\
    %
    R-ADJ3
    & $ (X \otimes Y)^\dagger \ \reduce\ X^\dagger \otimes Y^\dagger$ \\
    %
    R-ADJK0
    & $ \ZEROB(\sigma)^\dagger \ \reduce\ \ZEROK(\sigma) $ \\
    %
    R-ADJK1
    & $ \bra{t}^\dagger \ \reduce\ \ket{t} $ \\
    %
    R-ADJK2
    & $ (B \cdot O)^\dagger\ \reduce\ O^\dagger \cdot B^\dagger $ \\
    %
    R-ADJB0
    & $ \ZEROK(\sigma)^\dagger \ \reduce\ \ZEROB(\sigma) $ \\
    %
    R-ADJB1
    & $ \ket{t}^\dagger \ \reduce\ \bra{t} $ \\
    %
    R-ADJB2
    & $ (O \cdot K)^\dagger\ \reduce\ K^\dagger \cdot O^\dagger $ \\
    %
    R-ADJO0
    & $ \ZEROO(\sigma, \tau)^\dagger \ \reduce\ \ZEROO(\tau, \sigma) $ \\
    %
    R-ADJO1
    & $ \ONEO(\sigma)^\dagger \ \reduce\ \ONEO(\sigma)$ \\
    %
    R-ADJO2
    & $ (K \cdot B)^\dagger \ \reduce\ B^\dagger \cdot K^\dagger$ \\
    %
    R-ADJO3
    & $ (O_1 \cdot O_2)^\dagger \ \reduce\ O_2^\dagger \cdot O_1^\dagger $ \\
\end{ruletable}
